---
output: github_document
---

# Of Two Minds: A registered replication

Frederik Aust, Tobias Heycke, Benedek Kurdi, Pieter Van Dessel, Jeremy Cone, Melissa J. Ferguson, Xiaoqing Hu, Congjiao Jiang, Robert J. Rydell, Lisa Spitzer, Christoph Stahl, Christine Vitiello, & Jan De Houwer

<!-- ![](https://img.shields.io/badge/doi-10.31234/osf.io/v674w-yellow.svg)](https://doi.org/10.31234/osf.io/v674w) -->

[![](https://img.shields.io/badge/Open_access-Preprint-green.svg?logo=openaccess&logoColor=white)](https://doi.org/10.31234/osf.io/v674w) [![](https://img.shields.io/badge/OSF_repository-blue.svg?logo=osf&logoColor=white)](https://osf.io/v674w) [![](https://img.shields.io/badge/Language-R-orange?logo=r&logoColor=white)](https://osf.io/v674w)

<!-- [![](https://img.shields.io/badge/Code-Repository-green.svg)]() -->


<hr />

```{r}
#| label: setup
#| echo: false

library("targets")
knitr::opts_chunk$set(echo = FALSE)
```

This repository contains research products associated with the above publication.
We provide the experimental software and stimulus material that we are
permitted to share in the `material` directories of each experiment
(e.g. `otm1` or `otm2`).
The preregistration document for Experiment 1
is provided in `otm1/preregistration`.
The `results/data_raw` directories of each experiment contain all the raw
data; merged and processed data files can be found in
`results/data_processed`.
The R Markdown file `manuscript.Rmd` in the `paper` directory can be rendered to reproduce the manuscript using the R package `papaja`.

*Please see below for more details on the data, software requirements, computational requirements, and steps to reproduce the analyses.*


## Screen recordings

To give a vivid impression of the experimental procedure, an examplary screen recording of the procedure is available under `otm1/screen_recordings`.

1. `otm_1_sr_complete.mp4`: An example of the full procedure (please note that this is not a recording of any of the participants)
2. `otm_1_sr_overview.mp4`: A shorted version of the video to give a brief overview of all parts of the procedure (please note that the video does not reflect the actual procedure) 


## Data

The `results/data_raw` directories of each experiment contain all the raw
data.
For each participant there are seven files.
The following files are available for each participant (here shown for participant 101 of Experiment 1 at the University of Cologne):

| No. | Description | File name |
|-----|-------------|-----------|
| 1. | Demographics | `Data_Demographics_OTM_Cologne_101.dat` |
| 2. | Record of learning phase | `DataTrials_OTM_101.dat` |
| 3. | Attitude ratings | `DataEval_OTM_101.dat` |
| 4. | IAT data (trial-level) | `DataIAT_OTM_101.dat` |
| 5. | Recognition data | `DataMemTest_OTM_101.dat` |
| 6. | General log file | `OTM_Log_Cologne_101.dat` |
| 7. | Frame rate data | `OTM_ScreenLog_Cologne_101.dat` |

For a description of the variables in each file, please see the files `results/codebooks/data_raw/` of each experiment.

Merged and processed data files can be found in
`results/data_processed`.
The code used to merge and process the data is available in the **targets** pipelines in the `results` directories of each experiment (e.g., `_targets_otm1.r`; see below for details on how to run the analyses).
The data used for the analyses reported in the paper are (here shown for Experiment 1):

| No. | Description | File name |
|-----|-------------|-----------|
| 1. | Direct and indirect attitude scores separately for each block of the learning procedure and valence order | `otm1_attitudes.rds` |
| 2. | Direct and indirect attitude scores with block of learning procedure recoded such that 1 represents the block with positive behavior description and 2 the block with negative behavior description (used for Bayesian model comparisons) | `otm1_attitudes_collapsed.rds` |
| 3. | End-of-experiment recognition memory responses for briefly flashed words, demographic information, and responses to open-ended questions | `otm1_memory.rds` |

For a description of the variables in each dataset, please see the files `results/codebooks` of each experiment.


## Software requirements

### Experimental software

The experiment was programmed using PsychoPy 1.82.01 and 1.83.01.
*One of these versions must be installed to run the experiment.*
All files to reproduce the procedure can be found in the `material` directories of each experiment.

A folder called `data` (where output data is recorded), needs to be present
in the same folder as the Python script to run the experiment.

### Analyses

The version of R and all packages required to reproduce the anlysis are listed in the `DESCRIPTION` file.
It is required to install the archived version of `spatialfil` package (version 0.15):

```R
# From CRAN archive
remotes::install_version("spatialfil", dependencies = "0.15")

# Or from this repository
# remotes::install_local("./spatialfil_0.15.tar.gz")
```

When the repository is cloned, the other R package dependencies can be installed directly from the `DESCRIPTION` :

```R
# Install all remaining dependencies
remotes::install_deps()
```

## Computational requirements

Running all analyses may take a long time on a Desktop computer.
The following diagram shows the products of the **targets** pipelines for each experiment, their dependencies, and computation time.

### Experiment 1

```{r}
#| include: false

otm1_diagram <- tar_mermaid(
  label = c("time", "branches")
  , script = "./otm1/results/_targets_otm1.r"
  , store = "./otm1/results/_targets_otm1"
  , reporter = "silent"
)

otm2_diagram <- tar_mermaid(
  label = c("time", "branches")
  , script = "./otm2/results/_targets_otm2.r"
  , store = "./otm2/results/_targets_otm2"
  , reporter = "silent"
)
```

```{r}
#| label: otm1-dependencies
#| results: asis

cat("```mermaid\n")
cat(otm1_diagram, sep = "\n")
cat("\n```")
```

### Experiment 2

```{r}
#| label: otm2-dependencies
#| results: asis

cat("```mermaid\n")
cat(otm2_diagram, sep = "\n")
cat("\n```")
```


## Reproducing the analyses

To reproduce the manuscript and all analyses requires first running the **targets** pipelines for each experiment and then rendering the R Markdown file.


### **targets** pipelines

Parts of the analyses in this repository were performed using the R package [**targets**](https://cran.r-project.org/web/packages/targets/index.html) for reproducibility and efficiency.
Targets is a pipeline tool that allows to define the steps of an analysis and their dependencies in a way that makes it possible to rerun only the parts of the analysis that are affected by changes in the code or data.
The pipelines for each experiment are defined in the files `results/_targets_otm1.r` and `results/_targets_otm2.r` for Experiment 1 and Experiment 2, respectively.
Results of the analyses are stored in the directories `otm1/_targets_otm1/objects` and `otm2/_targets_otm2/objects`, and can be loaded using `targets::tar_load()` or `targets::tar_read()`.
This may be useful to inspect intermediate results (especially for the computationally expensive posterior samples of our Bayesian models) or to rerun only parts of the analyses (e.g., changing a plot).

#### Parallel or distributed computing

The pipelines are configured to run the analyses on a desktop computer, but they can be adapted to run on a cluster (e.g., by using `targets::tar_make_future()` for parallelisation and configuring parallel workers in `otm1/_targets_otm1.r` or `otm2/_targets_otm2.r`).

To define a parallel computing plan, use the `future` package and set up a plan in the `_targets_otm1.r` or `_targets_otm2.r` file (e.g., using `future::plan(future::multisession, workers = 4)` for local parallel processing with 4 cores).
To control the number of workers (computers or local processes) used for the analysis, change the **targets** `workers` option in `_targets.yaml` (`workers: 4` in this example).
  
To fully deactivate parallel processing, set `workers: 1` in `_targets.YAML` and `distributed <- FALSE` in `_make.sh`.


#### Running the pipelines

To run the pipelines, execute the file `_make.sh` in the root directory of the repository.
First, set the `project` variable in `_make.sh` to `otm1` and then execute the file in a terminal to run the analysis for Experiment 1 (*this may take a long time, see above*):

```bash
sh ./_make.sh
```

Alternatively, run the R code in `_make.sh` directly in a vanilla R session.

Then, set the `project` variable to `otm2` to run the analysis for Experiment 2.

The R Markdown files `analysis1.Rmd` and `analysis2.Rmd` in the `results` directories will be rendered in the final step of the pipelines.
These reports contain show results of the analyses.


### Rendering the manuscript

Once all targets have been run, the R Markdown file `manuscript.Rmd` in the `paper` directory can be rendered to reproduce the manuscript using the R package `papaja`.

```R
rmarkdown::render("analysis_and_paper/manuscript.Rmd")
```

The R Markdown file `supplement.Rmd` in the `paper` directory can be rendered to reproduce the supplementary material.

Alternatively, the manuscript and supplementary material can be rendered by running the corresponding targets in the pipeline by setting the `project` variable in `_make.sh` to `paper` and executing `sh ./_make.sh` in a terminal or running the R code in `_make.sh` directly in a vanilla R session.


## Preferred citation

```{r}
#| label: citation
#| echo: false
#| comment: ""

cffr::as_bibentry(x = "CITATION.cff") |>
  toBibtex()
```


## Licensing information

| Product | License |
| ------- | ------- |
| Code | [MIT](http://opensource.org/licenses/MIT) 2025 Frederik Aust & Tobias Heycke |
| Data | [CC0](https://creativecommons.org/publicdomain/zero/1.0/) |
| Experimental software | [MIT](http://opensource.org/licenses/MIT) 2025 Frederik Aust & Tobias Heycke |
| Stimulus material | [CC0](https://creativecommons.org/publicdomain/zero/1.0/) |

<!-- | Manuscript | [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/) | -->


## Contact

Frederik Aust

Research Methods and Experimental Psychology,<br />
Department of Psychology,<br />
University of Cologne

frederik.aust@uni-koeln.de
