---
title           : "Of Two Minds: A registered replication"
shorttitle      : "Replication of Rydell et al."

author: 
  - name          : Frederik Aust
    affiliation   : "1,9"
    corresponding : yes    
    address       : "Herbert-Lewin-Str. 2, 50931 Cologne, Germany"
    email         : "frederik.aust@uni-koeln.de"
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Resources
      - Software
      - Supervision
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
  - name          : Tobias Heycke
    affiliation   : "1,2"
    role:
      - Conceptualization
      - Data curation
      - Investigation
      - Methodology
      - Project administration
      - Software
      - Supervision
      - Validation
      - Writing - original draft
      - Writing - review & editing
  - name          : Benedek Kurdi
    affiliation   : "3,10,12"
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Supervision
      - Writing - original draft
      - Writing - review & editing
  - name          : Pieter Van Dessel
    affiliation   : 5
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Supervision
      - Validation
      - Writing - review & editing
  - name          : Jeremy Cone
    affiliation   : 8
    role:
      - Investigation
      - Resources
      - Validation
  - name          : Melissa J. Ferguson
    affiliation   : 10
    role:
      - Investigation
      - Resources
      - Validation
  - name          : Xiaoqing Hu
    affiliation   : 6
    role:
      - Investigation
      - Resources
  - name          : Congjiao Jiang
    affiliation   : "4,14"
    role:
      - Investigation
      - Resources
  - name          : Robert J. Rydell
    affiliation   : 7
    role:
      - Methodology
      - Resources
  - name          : Lisa Spitzer
    affiliation   : "1,13"
    role:
      - Investigation
      - Software
      - Writing - review & editing
  - name          : Christoph Stahl
    affiliation   : 1
    role:
      - Funding acquisition
      - Resources
      - Supervision
      - Writing - review & editing
  - name          : Christine Vitiello
    affiliation   : "4,11"
    role:
      - Investigation
      - Resources
  - name          : Jan De Houwer
    affiliation   : 5
    role:
      - Conceptualization
      - Funding acquisition
      - Resources
      - Supervision
      - Writing - review & editing

affiliation:
  - id            : 1
    institution   : University of Cologne
  - id            : 2
    institution   : Leibniz Institute for the Social Sciences (GESIS)
  - id            : 3
    institution   : Harvard University 
  - id            : 4
    institution   : University of Florida 
  - id            : 5
    institution   : Ghent University 
  - id            : 6
    institution   : The University of Hong Kong 
  - id            : 7
    institution   : Indiana University
  - id            : 8
    institution   : Williams College
  - id            : 9
    institution   : University of Amsterdam
  - id            : 10
    institution   : Yale University
  - id            : 11
    institution   : Air Force Research Laboratory
  - id            : 12
    institution   : University of Illinois Urbana--Champaign
  - id            : 13
    institution   : Leibniz Institute for Psychology (ZPID)
  - id            : 14
    institution   : Peking University

abstract: "(ref:abstract)"
  
authornote: |
  Cleared Distro A, Originator Reference Number: RH-26-127880, Case Reviewer: Mary Allen, Case Number: AFRL-2026-0840. The experiment investigation and resource collection were conducted prior to the author C.V. joining the U.S. Department of Defense. The views presented herein are the author(s) and not necessarily the views of the DoD or its components.

note: |
  \clearpage

keywords          : "evaluative learning, subliminal influence, implicit learning, replication"
#wordcount         : "X"

bibliography      : ["references.bib", "r-references.bib"]
#appendix          : "appendix.Rmd"

header-includes:
  - \interfootnotelinepenalty=10000
  
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes
mask              : no
draft             : no
quote_labels      : yes

link-citations    : yes
linkcolor         : blue
urlcolor          : blue

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
# output            : papaja::apa6_docx
---

```{r}
#| label: load-packages
#| include: false
#| warning: false

library("magrittr")
library("tidyr")
library("dplyr")
# library("assertthat")

library("targets")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("afex")
library("emmeans")
library("BayesFactor")
library("MBESS")
library("effectsize")
library("Superpower")

source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")

source("../R/effect_sizes.r")
source("../R/apa_print_ps.r")
source("../R/apa_print_bf.r")
source("../R/error_in_variables.r")
```

```{r}
#| label: analysis-preferences

# Set seed for random number generator
set.seed(315054738)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Always report MSE for ANOVA
options(papaja.mse = TRUE)

# Use multivariate models for emmeans contrasts and post-hoc tests
afex_options(emmeans_model = "multivariate")

# Default ggplot theme
theme_set(theme_apa())
```

```{r}
#| label: cache-preferences

# Automatically manage cache dependencies
knitr::opts_chunk$set(autodep = TRUE)
knitr::dep_auto()

# Ignore changes to comments in cached chunks
knitr::opts_chunk$set(cache.comments = FALSE)

# Discard cache if random seed changes
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Show NA as "" in tables
options(knitr.kable.NA = "")

# Targets cache
otm1_store <- "../otm1/results/_targets_otm1"
otm2_store <- "../otm2/results/_targets_otm2"
```

```{r}
#| label: otm-load-data-and-sample-sizes

# Experiment 1
otm1_eval <- tar_read(otm1_eval2, store = otm1_store)
otm1_iat <- tar_read(otm1_iat2, store = otm1_store)
otm1_attitudes <- tar_read(otm1_attitudes, store = otm1_store)
otm1_mem <- tar_read(otm1_memory, store = otm1_store)

otm1_n <- as.integer(nlevels(otm1_attitudes$ParticipantNumber))

# Experiment 2
otm2_attitudes <- tar_read(otm2_attitudes, store = otm2_store)
otm2_mem <- tar_read(otm2_memory, store = otm2_store) |> # TODO: remove when targets have been rerun
  dplyr::mutate(
    Gender = case_when(
      grepl("^(f|cis-f|w)", Gender, ignore.case = TRUE) ~ "female"
      , grepl("^m", Gender, ignore.case = TRUE) ~ "male"
      , grepl("non", Gender, ignore.case = TRUE) ~ "nonbinary"
    )
  )

# Sample sizes prior to exclusions
otm2_n_list <- tar_read(otm2_eval, store = otm2_store) |>
  pull(Location) |>
  table() |>
  (\(x) x / 2)()

# Total sample size after exclusions
otm2_n_total <- sum(table(otm2_mem$Location))
```


(ref:abstract) Several dual-process theories of social evaluation posit that implicit (or automatic) and explicit (or non-automatic) evaluations reflect distinct attitudes acquired via qualitatively different learning processes. Consequently, one may explicitly like a person but dislike them implicitly. Rydell et al. (2006) reported a striking demonstration of this dissociation: Briefly flashed negative words paired with a person described as behaving positively produced positive ratings of that person but negative Implicit Association Test scores. However, Heycke et al. (2018) could not replicate this dissociation. In two new replication attempts ($N = `r otm1_n + otm2_n_total`$) across four countries and three languages, with words flashed between 13 and 27 ms, we too found overwhelming evidence against the dissociation between directly and indirectly measured evaluations. We conclude that the dissociative evaluative learning effect reported by Rydell et al. (2006) is replicably non-replicable.



Are people's explicit and implicit evaluations of an object or person always consistent with one another?
Or is it possible that we like a person explicitly but simultaneously dislike them implicitly?
One way to investigate this question is to compare two families of evaluative measures: direct measures (e.g., Likert scales) that assumedly elicit relatively more explicit, conscious, effortful, and controllable evaluations (hereafter explicit evaluations), on the one hand, and indirect measures [such as the Implicit Association Test [IAT], @greenwald_measuring_1998] that assumedly elicit relatively more implicit, unconscious, effortless, and uncontrollable evaluations (hereafter implicit evaluations), on the other hand.
Indeed, several studies have shown dissociations between direct and indirect measures [@harmon-jones_what_2019].
Such evidence has been critical in supporting dual-process theories positing that explicit and implicit evaluations reflect different sets of attitudes that are acquired via two distinct processes.[^attitude_definition]


[^attitude_definition]:
By *attitude* we mean latent knowledge representations that underlie the behavioral expression of *evaluations* on direct and indirect measures [@cunningham_attitudes_2007].


An influential dual-process theory is the Systems of Evaluation Model [SEM, @mcconnell_systems_2014; @mcconnell_forming_2008; @rydellUnderstandingImplicitExplicit2006]. 
This theory assumes that implicit evaluations emerge from mental associations that develop without conscious awareness or control, from the co-occurrence of stimuli with valenced events.
For example, positive associations may develop simply because a person repeatedly wears a shirt in one’s favorite color.
In contrast, explicit evaluations are thought to reflect propositional representations that emerge from conscious, attention-demanding reasoning processes.
For example, negative propositions may develop as a result of learning that the person holds political opinions that clash with one’s own views.
Hence, under this theory, a double dissociation between direct and indirect measures of evaluation is expected, with the former reflecting only consciously formed propositions and the latter reflecting only unconsciously formed associations.

As a test of this model, @rydell_two_2006 contrasted two different learning pathways experimentally.
In the experiment, participants learned about an unfamiliar person called Bob.
Each trial started with a brief (25 ms) flash of a positive or negative word, not intended to be consciously registered by participants.
Then a photograph of Bob was presented alone for 250 ms before a positive or negative behavioral statement was added to the display.
The statement was clearly visible until participants made a guess as to whether the behavior was characteristic or uncharacteristic of Bob.
Participants immediately received feedback, which implied that Bob was a good or bad person.
Crucially, this behavioral information was always opposite in valence to the briefly flashed word.
In line with the predictions of the SEM, explicit evaluations of Bob, measured via self-report, reflected predominantly the valence of the behavioral information.
More intriguingly, implicit evaluations, measured via the IAT, reflected predominantly the valence of the words that had been briefly flashed prior to the photograph of Bob.

This finding has been influential in support of the SEM and other dual-process theories [e.g., @gawronskiAssociativePropositionalEvaluation2011]. 
However, beyond this prominent result, empirical evidence for dual evaluative learning processes remains weak overall [@corneilleAssociativeAttitudeLearning2018a]. 
The absence of compelling evidence that implicit evaluations emerge from unconsciously formed associations has allowed for a different, more parsimonious, account to be popularized: that both implicit and explicit evaluations reflect propositional knowledge [e.g., @de_houwer_propositional_2018]. 
Crucially, many prominent single-process propositional theories assume that propositional learning requires conscious awareness [@mitchellPropositionalNatureHuman2009]. 
As such, the result reported by @rydell_two_2006, where implicit evaluations reflected predominantly unconsciously formed associations, is particularly difficult to reconcile with these accounts.
Under most propositional theories, both direct (self-report) measures and indirect measures (such as the IAT) should reflect propositional knowledge that emerges from conscious, attention-demanding reasoning processes.

Given the theoretical issues at stake, a replication of the double dissociation reported by  @rydell_two_2006 is critical. 
If the double dissociation is replicated, such a result would lend credence to strong forms of dual-process theories positing that implicit and explicit evaluations reflect different types of (associative and propositional) representations that are acquired via different learning pathways.
Moreover, such a finding would provide evidence in favor of subliminal associative learning, a phenomenon for which current evidence is weak at best [@corneilleAssociativeAttitudeLearning2018a]. 
On the other hand, if the finding by @rydell_two_2006 does not replicate, and both direct and indirect measures are found to reflect the valence of the consciously processed behavioral information, such a result would strengthen confidence in single-process propositional theories of evaluation.
After all, these theories argue that both implicit and explicit evaluations largely reflect the same consciously formed propositions.

In two recent experiments, the double dissociation reported by @rydell_two_2006 did not replicate [@heycke_two_2018]. 
Instead, both direct and indirect measures consistently reflected the valence of the behavioral information.
At present, it is unclear whether these results point towards boundary conditions or call into question the replicability of the original study more generally.
This ambiguity is due to the fact that materials were translated into German and stimuli were presented for a duration different from the original study.
Here, we rigorously test the replicability of the double dissociation by closely adhering to the original procedure.
To ensure its informativeness, the current replication attempt was conducted jointly by an international collective of experts on evaluative learning and indirect measures of evaluation.
Among the collaborators were the first author of the original study and authors of the previous replication attempts.
To explore the generality of the results, we collected data in multiple countries and languages.
A first preregistered experiment was conducted in Belgium, Germany and the USA.
In the subsequent registered replication, we used the insights from the first experiment to adjust the procedure to closely replicate the stimulus visibility conditions of the original study.


# Research transparency statement

## General disclosures

**Conflicts of interest**:
Frederik Aust is a member of the Psychological Science Editorial team (i.e., STAR editor) at the time of Stage-2 submission.
Benedek Kurdi is chair of the Scientific Advisory Board of Project Implicit, a 501(c)(3) non-profit organization and international collaborative of researchers who are interested in implicit social cognition.
All other authors declare no conflicts of interest.
**Funding**:
This research has been supported by the Deutsche Forschungsgemeinschaft (Grant ST-1269/3-2 awarded to Christoph Stahl).
Jan De Houwer is supported by Methusalem Grant 01M00209 of Ghent University.
**Artificial intelligence**: Microsoft's Copilot was used as intelligent copyediting tool during the creation of this article.
No other artificial-intelligence-assisted technologies were used in this research or the creation of this article.
**Ethics**: This research received approval from the Yale University institutional review board (ID: 2000031518).

## Experiment 1 disclosures

**Preregistration**: The hypotheses, methods, and analysis plans were preregistered on the Open Science Framework (https://osf.io/qftkj/) on January 29th, 2018, prior to data collection, which began on January 30th, 2018. We describe deviations in Table\ \@ref(tab:otm-preregistration-deviation-table).
**Materials**: All study materials are publicly available (https://osf.io/8m3xb/).
**Data**: All primary data are publicly available (https://osf.io/8m3xb/). 
**Analysis scripts**: All analysis scripts are publicly available (https://osf.io/8m3xb/).

## Experiment 2 disclosures

**Preregistration**: The hypotheses, methods, and analysis plans were preregistered as a Stage-1 registered report (https://doi.org/10.31234/osf.io/v674w) on November 9th, 2020, prior to data collection, which began on September 23rd, 2021. We describe deviations in Table\ \@ref(tab:otm-preregistration-deviation-table).
**Materials**: All study materials are publicly available (https://osf.io/8m3xb/).
**Data**: All primary data are publicly available (https://osf.io/8m3xb/). 
**Analysis scripts**: All analysis scripts are publicly available (https://osf.io/8m3xb/).


```{r}
#| label: otm1-child
#| child: "./otm1.Rmd"

```

```{r}
#| label: otm2-child
#| child: "./otm2.Rmd"

```


# Exploratory analysis: Joint analysis of Experiments 1 and 2

(ref:otm-joint-eiv-regression) Scatterplot with marginal histograms showing results from error-in-variables regression analysis [@Klauer_Draine_Greenwald_1998] predicting pooled learning block differences in IAT scores from recognition accuracy of briefly flashed words.

```{r}
#| label: otm-joint-eiv-regression-plot
#| fig-cap: "(ref:otm-joint-eiv-regression)"
#| fig-width: 6
#| fig-height: 4.25
#| cache: true

otm1_iat_delta <- full_join(
  otm1_attitudes_delta
  , select(otm1_mem, ParticipantNumber, Accuracy)
  , by = join_by(ParticipantNumber)
) %>% 
  filter(Measure == "IATscore") |>
  mutate(
    Duration = if_else(Location == "Harvard", "24", "27") |>
      factor(levels = c("13", "20", "24", "27"))
  )

otm2_iat_delta <- full_join(
  otm2_attitudes_delta
  , select(otm2_mem, ParticipantNumber, Accuracy)
  , by = join_by(ParticipantNumber)
) %>% 
  filter(Measure == "IATscore") |>
  mutate(
    Duration = factor(Duration, levels = c("13", "20", "24", "27"))
  )

otm_iat_delta <- full_join(
  otm1_iat_delta
  , otm2_iat_delta
)

joint_scatterplot <- otm_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta, color = Duration)) +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black", method.args = list(n.optim = 50)) +
  # geom_smooth(method = "lm", color = "black") +
  # geom_smooth(color = "blue") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(ital*ic*(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  scale_color_viridis_d(option = "B", direction = -1, end = 0.8) +
  scale_fill_viridis_d(option = "B", direction = -1, end = 0.8) +
  guides(
    color = guide_legend(title = "Flash duration (ms)", direction = "horizontal")
    , fill = guide_legend(title = "Flash duration (ms)", direction = "horizontal")
  ) +
  theme_apa(box = TRUE) +
  theme(
    legend.justification = c(1, 0)
    , legend.position = "inside"
    , legend.position.inside = c(0.95, 0.05)
    , legend.title.position = "top"
    , legend.title = element_text(hjust = 0.5)
    , legend.background = element_blank()
    , legend.key.height = unit(1.1, "line")
    , legend.key.width = unit(1.1, "line")
    , plot.margin = margin()
  )

# Define marginal histogram
marginal_distribution <- function(x, var, group) {
  ggplot(x, aes_string(x = var, fill = group, color = group)) +
    # geom_histogram(bins = 30, alpha = 0.4, position = "dodge", aes(y = after_stat(density))) +
    geom_density(alpha = 0.4, size = 0.1) +
    scale_color_viridis_d(option = "B", direction = -1, end = 0.8) +
    scale_fill_viridis_d(option = "B", direction = -1, end = 0.8) +
    guides(fill = "none", color = "none") +
    theme_void() +
    theme(plot.margin = margin())
}

# Set up marginal histograms
x_hist <- marginal_distribution(otm_iat_delta, "Accuracy", "Duration")
y_hist <- marginal_distribution(otm_iat_delta, "delta", "Duration") +
  coord_flip()

# Align histograms with scatterplot
aligned_x_hist <- align_plots(x_hist, joint_scatterplot, align = "v")[[1]]
aligned_y_hist <- align_plots(y_hist, joint_scatterplot, align = "h")[[1]]

# Arrange plots
plot_grid(
  aligned_x_hist
  , NULL
  , joint_scatterplot
  , aligned_y_hist
  , ncol = 2
  , nrow = 2
  , rel_heights = c(0.2, 1)
  , rel_widths = c(1, 0.15)
)
```

```{r}
#| label: otm-joint-eiv-regression

otm_iat_eiv_res <- otm_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 50)  |>
  apa_print()
```

The concern that motivated Experiment 2 was that there was reason to believe that some participants consciously perceived some briefly flashed words in Experiment 1, which may have affected the results.
The shortened presentation durations in Experiment 2 did not substantiate this concern. 
To dispel this concern more conclusively, we performed an additional non-preregistered analysis of the data from both experiments:
We examined whether individual differences in recognition accuracy of the briefly flashed words moderated the effect of briefly flashed words on indirectly measured evaluations.
In an error-in-variables regression analysis, we predicted pooled learning block differences in IAT scores from recognition accuracy of briefly flashed words [@Klauer_Draine_Greenwald_1998], Figure\ \@ref(fig:otm-joint-eiv-regression-plot).
However, even at the individual level we were unable to detect an association between recognition accuracy of briefly flashed words and IAT score differences, `r otm_iat_eiv_res$full_result[[2]]`.
Critically, even individuals with recognition accuracy at or around chance level (0.5) did not show the reversal of IAT score differences indicative of learning from the briefly flashed words.


# General Discussion

Twenty years ago, @rydell_two_2006 reported an influential double dissociation between directly measured evaluations (ratings scales) and indirectly measured evaluations (IAT) of the same novel target: Evaluative ratings reflected the valence of behavioral statements about the target, whereas IAT scores reflected the opposite valence of briefly flashed words co-occurring with the target.
This finding has been influential in support of the SEM and other dual-process theories of evaluation [e.g., @gawronskiAssociativePropositionalEvaluation2011].
However, @heycke_two_2018 reported two experiments in which this double dissociation did not replicate.
Here, we investigated if this failure to replicate points towards boundary conditions or instead calls into question the replicability of the original study more generally.

We conducted a large-scale replication effort involving an international collective of researchers with expertise in evaluative learning and indirect measures of evaluation, including the first author of the original study and the authors of previous replication attempts.
Across two laboratory experiments, we collected a large sample of a total of $N = `r otm1_n + otm2_n_total`$ participants from multiple countries (Belgium, Germany, Hong Kong, and USA) and in multiple languages (Dutch, English, and German).
Additionally, we varied the presentation duration of the briefly flashed words (13 ms, 20 ms, 24 ms, and 27 ms) to not only exactly replicate the original procedure but also ensure that we closely mimic the stimulus visibility conditions of the original learning task (specifically, approximately at-chance recognition of the briefly flashed words at the end of the experiment).
Across all conditions and experiments, we found strong evidence against a dissociation between directly and indirectly measured evaluations.
Instead, both measures reflected the valence of behavioral statements, although the self-report measure consistently produced stronger effects than the IAT, presumably due to differences in psychometric properties.
Moreover, individual differences in recognition accuracy of the briefly flashed words did not moderate indirectly measured evaluations, thus providing further evidence that a dissociation is not to be expected for other presentation durations.

Theoretical implications should be drawn with appropriate caution.
The present findings provide strong evidence against a key empirical finding predicted by the SEM and taken to support related dual-process theories.
Thus, the results obtained here further weaken the already limited evidential base of these theories [@corneilleAssociativeAttitudeLearning2018a].
Conversely, the findings remove an important challenge to the more parsimonious single-process propositional theories [e.g., @Houwer2014; @mitchellPropositionalNatureHuman2009].
However, these  experiments should not be viewed as conclusive tests of single- versus dual-process theories of evaluative learning.
Notably, we cannot rule out the possibility that dissociations between implicit and explicit evaluations could be observed in other experimental designs—including studies that similarly pit learning effects resulting from stimuli with brief versus longer presentation durations.

On this note, we recommend that relevant future research adhere to current standards for research on unconscious processing [@Stockart2025; @Schmidt2026].
First, researchers should be mindful that neither direct measures nor indirect measures of evaluation are process pure [@Conrey2005; @Jacoby1991] and dissociations between them may reflect factors other than distinct automatic and non-automatic processes.
Second, retrospective measures of stimulus awareness are imperfect proxies of awareness during the learning task and their use requires careful consideration [e.g., @Gawronski2012; @Shanks1994; @Stockart2025].
For example, assessments of awareness should distinguish between valence and identity awareness [@Stahl2009].
Third, future research may benefit from calibrating stimulus presentation to individual differences in thresholds for conscious perception [e.g., @Chen2025; @Greenwald1989].

To conclude, across two high-powered experiments conducted across multiple countries and languages, we found overwhelming evidence against the dissociative evaluative learning effect originally reported  by @rydell_two_2006.
Together with results from previous replication attempts by @heycke_two_2018 these results show that this effect is replicably non-replicable and should no longer be treated as evidence in support of dual-process theories of evaluative learning.


\newpage

# References

```{r}
#| label: create-r-references

# r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parskip}{0pt}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
