---
title           : |
  Supplementary online material for
    
  *Of Two Minds: A registered replication*

shorttitle      : "Replication of Rydell et al."

author: 
  - name          : Frederik Aust
    affiliation   : "1,9"
    corresponding : yes    
    address       : "Herbert-Lewin-Str. 2, 50931 Cologne, Germany"
    email         : "frederik.aust@uni-koeln.de"
  - name          : Tobias Heycke
    affiliation   : "1,2"
  - name          : Benedek Kurdi
    affiliation   : "3,10,12"
  - name          : Pieter Van Dessel
    affiliation   : 5
  - name          : Jeremy Cone
    affiliation   : 8
  - name          : Melissa J. Ferguson
    affiliation   : 10
  - name          : Xiaoqing Hu
    affiliation   : 6
  - name          : Congjiao Jiang
    affiliation   : "4,14"
  - name          : Robert J. Rydell
    affiliation   : 7
  - name          : Lisa Spitzer
    affiliation   : "1,13"
  - name          : Christoph Stahl
    affiliation   : 1
  - name          : Christine Vitiello
    affiliation   : "4,11"
  - name          : Jan De Houwer
    affiliation   : 5

affiliation:
  - id            : 1
    institution   : University of Cologne
  - id            : 2
    institution   : Leibniz Institute for the Social Sciences (GESIS)
  - id            : 3
    institution   : Harvard University 
  - id            : 4
    institution   : University of Florida 
  - id            : 5
    institution   : Ghent University 
  - id            : 6
    institution   : The University of Hong Kong 
  - id            : 7
    institution   : Indiana University
  - id            : 8
    institution   : Williams College
  - id            : 9
    institution   : University of Amsterdam
  - id            : 10
    institution   : Yale University
  - id            : 11
    institution   : Air Force Research Laboratory
  - id            : 12
    institution   : University of Illinois Urbana--Champaign
  - id            : 13
    institution   : Leibniz Institute for Psychology (ZPID)
  - id            : 14
    institution   : Peking University
    

bibliography      : ["references.bib", "r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "doc"
output            : papaja::apa6_pdf
---

```{r}
#| label: load-packages
#| include: false
#| warning: false

library("magrittr")
library("tidyr")
library("dplyr")
library("assertthat")

library("targets")

library("papaja")
library("ggplot2")
library("ggforce")
library("cowplot")

library("lmerTest")
library("emmeans")
library("BayesFactor")

library("Superpower")

source("https://gist.githubusercontent.com/crsh/be88be19233f1df4542aca900501f0fb/raw/f258053d144681bd4a5b86ed0956da7dc3f380ee/gglegend.R")
source("../R/effect_sizes.r")
source("../R/error_in_variables.r")
```

```{r}
#| label: analysis-preferences

# Set seed for random number generator
set.seed(315054738)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Use effect coding
options(contrasts = c("contr.sum", "contr.poly"))

# Default ggplot theme
theme_set(theme_apa())

# Number of MCMC samples for Bayesian analysis
otm1_n_mcmc_samples <- 1e6
```

```{r}
#| label: cache-preferences

# Automatically manage cache dependencies
knitr::opts_chunk$set(autodep = TRUE)
knitr::dep_auto()

# Ignore changes to comments in cached chunks
knitr::opts_chunk$set(cache.comments = FALSE)

# Discard cache if random seed changes
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)

# Show NA as "" in tables
options(knitr.kable.NA = "")

# Targets cache
otm1_store <- "../otm1/results/_targets_otm1"
otm2_store <- "../otm2/results/_targets_otm2"
```

\newpage

In the following we report details on our power analyses, the model specifications used for the Bayesian model comparisons, and additional secondary analyses.


# Sensitivity of our design

```{r}
#| label: otm1-power-results

som_cache <- "./manuscript_cache/latex/"

rydell_pes <- 0.1
rydell_f <- 4.78
rydell_n <- 50
rydell_dz <- pes_to_dz(rydell_pes, rydell_n, n_groups = 2)

heycke_t <- c(2.54, 1.45)
heycke_n <- c(28, 26)
heycke_dz <- heycke_t / sqrt(heycke_n)
heycke_pes <- dz_to_pes(heycke_dz, heycke_n, n_groups = 1)

otm1_n_power <- knitr::load_cache(label = "otm1-power", object = "otm1_n_power", path = som_cache) * 2
otm1_pes <- knitr::load_cache(label = "otm1-power", object = "otm1_pes", path = som_cache)
otm1_dz <- knitr::load_cache(label = "otm1-power", object = "otm1_dz", path = som_cache)


otm2_n_power <- knitr::load_cache(label = "otm2-omnibus-power", object = "otm2_n_power", path = som_cache) * 4
otm2_pes <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes", path = som_cache)
otm2_dz <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz", path = som_cache)
otm2_pes_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_between_collapsed", path = som_cache)
otm2_dz_between_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_between_collapsed", path = som_cache)
otm2_pes_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_pes_collapsed", path = som_cache)
otm2_dz_collapsed <- knitr::load_cache(label = "otm2-contrast-power", object = "otm2_dz_collapsed", path = som_cache)
```

As noted in the main text, our assessment of the statistical senstivitiy of our design focused the tests of simple *learning block* effects, because they are of primary theoretical interest and less sensitive than the test of the interaction.
In Experiment 1, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm1_dz`$ ($\eta_p^2 = `r printp(otm1_pes)`$).
In Experiment 2, our planned contrasts had 95% power to detect learning block effects as small as $\delta_z = `r otm2_dz`$ ($\eta_p^2 = `r printp(otm2_pes)`$) or as small as $\delta_z = `r otm2_dz_between_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_between_collapsed)`$) and $\delta_z = `r otm2_dz_collapsed`$ ($\eta_p^2 = `r printp(otm2_pes_collapsed)`$) when pooling participants across one or both between-participant factors ($N = `r otm2_n_power * 4`$, $\alpha = .05$, two-sided tests).
Figure\ \@ref(fig:power-curve-plot) illustrates the implied sensitivity of our designs in units of Cohen's $\delta$ as a function of the assumed repeated-measures correlation $\rho$.
Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.

(ref:otm1-power-curve) Sensitivity curves for simple learning block effects in Experiment 1 (**A**) and Experiment 2 (**B**) as a function of the assumed repeated measures correlation.
Simple contrast are estimated within each *flashed word presentation duration*-*valence order* combination (not adjusted for multiple comparisons).
Collapsed contrasts pool participants across one or both  of the between subject factors (i.e., *flashed word presentation duration* and *valence order*).
$\delta_z$-values in the legend correspond to 95% and 80% power.
Note that these are conservative estimates as they do not take into account the additional 60 participants from our pilot study that we included in the analysis.
The grey dashed line at the top represents the smallest learning block difference reported by Rydell et al. [$d_z = `r rydell_dz`$; @rydell_two_2006].

```{r}
#| label: power-curve-plot
#| fig-width: 7
#| fig-height: 8
#| fig-cap: "(ref:otm1-power-curve)"

rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

otm1_power_curve_plot <- otm1_power_curve %>% 
  mutate(
    power = relevel(factor(power), "0.95")
  ) %>% 
  ggplot(aes(x = rho, y = delta, group = power, linetype = power)) +
  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  # annotate("text", x = 1, y = 0.9, label = paste0("list(alpha ==~\".05\", italic(N) ==", otm1_n, ", epsilon == 1)"), parse = TRUE, hjust = 1, vjust = 0.5) +
  ylim(c(0, 1)) +
  scale_linetype_discrete(
    labels = c(
      bquote(.(unique(otm1_power_curve$power)[1])~~(delta[z] == .(printnum(otm1_dz))))
      , bquote(.(unique(otm1_power_curve$power)[2])~~(delta[z] == .(printnum(otm1_dz2))))
    )
  ) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  ggtitle("", subtitle = bquote(list(italic(N) == .(otm1_n_power*2), alpha ==~".05", "two-sided"))) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    # , legend.position = c(0.99, 0.99)
    , legend.justification = "top"
    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )

rydell_power_curve <- tibble(
  rho = seq(-1, 1, length.out = 100)
  , delta = c(
    dz_to_f(rydell_dz, unique(rho)) * 2
    # dz_to_f(mean(heycke_dz), unique(rho)) * 2
  )
  , power = NA
)

otm1_power_curve <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , delta = c(
    dz_to_f(otm1_dz, unique(rho)) * 2
    , dz_to_f(otm1_dz2, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
)

otm2_power_curve_plot <- tibble(
  rho = rep(seq(-1, 1, length.out = 100), 2)
  , otm2_delta_simple = c(
    dz_to_f(otm2_dz, unique(rho)) * 2
    , dz_to_f(otm2_dz2, unique(rho)) * 2
  )
  , otm2_delta_between_collapsed = c(
    dz_to_f(otm2_dz_between_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_between_collapsed, unique(rho)) * 2
  )
  , otm2_delta_collapsed = c(
    dz_to_f(otm2_dz_collapsed, unique(rho)) * 2
    , dz_to_f(otm2_dz2_collapsed, unique(rho)) * 2
  )
  , power = rep(c("0.95", "0.80"), each = length(rho)/2)
) %>% 
  pivot_longer(cols = matches("otm"), names_to = "contrast", values_to = "delta") %>%
  mutate(
    power = relevel(factor(power), "0.95")
    , contrast = gsub("otm2_delta_", "", contrast)
    , contrast = gsub("_", " ", contrast)
    , contrast = factor(contrast, levels = c("simple", "between collapsed", "collapsed"))
  ) %>% 
  ggplot(aes(x = rho, y = delta, color = contrast, group = interaction(power, contrast), linetype = power)) +
  # ggplot(aes(x = rho, y = delta, color = power, group = power)) +
  # geom_line(data = otm1_power_curve, aes(group = power, linetype = power, color = "simple"), alpha = 0.3) +
  geom_line(data = rydell_power_curve, aes(group = power), color = grey(0.8), linetype = "dashed") +
  geom_line() +
  scale_color_viridis_d(
    end = 0.8
    , labels = c(
      bquote("Simple                "~delta[z] %in% "["*.(printnum(otm2_dz))*", "*.(printnum(otm2_dz2))*"]")
      , bquote("Collapsed once   "~delta[z] %in% "["*.(printnum(otm2_dz_between_collapsed))*", "*.(printnum(otm2_dz2_between_collapsed))*"]")
      , bquote("Collapsed twice   "~delta[z] %in% "["*.(printnum(otm2_dz_collapsed))*", "*.(printnum(otm2_dz2_collapsed))*"]")
    )
  ) +
  ylim(c(0, 1)) +
  labs(
    x = bquote("Correlation between learning blocks ["*rho*"]")
    , y = bquote("Learning block difference [Cohen's"~delta*"]")
    , color = "Contrast"
    , linetype = bquote("Power"~"["*1 - beta*"]")
  ) +
  ggtitle("", subtitle = bquote(list(italic(N) == .(otm2_n_power*4), alpha ==~".05", "two-sided"))) +
  theme_apa(box = TRUE) + 
  theme(
    panel.grid.major.x = element_line()
    , panel.grid.major.y = element_line()
    , panel.grid.minor.x = element_line()
    , panel.grid.minor.y = element_line()
    # , legend.position = c(0.99, 0.99)
    , legend.justification = "top"
    # , legend.background = element_rect(fill = scales::alpha("white", 0.5))
  )

plot_grid(
  plot_grid(otm1_power_curve_plot, NULL, rel_widths = c(1, 1 - 5.65/7))
  , otm2_power_curve_plot
  , nrow = 2
  , ncol = 1
  , labels = "AUTO"
)
```


# Experiment 1

In the following we report details on our power analysis, the model specification used for the Bayesian model comparisons, and additional secondary analyses.
We report results from the linear mixed model analysis of the IAT response times, from prior sensitivity analyses for the Bayesian model comparisons, and from an exploratory analysis of the relationship between the recognition accuracy of briefly flashed words and indirectyl measured evaluations.
Table\ \@ref(tab:otm1-participant-table) summarizes the participants' demographics separately for each location of data collection.

```{r}
#| label: otm1-load-data

otm1_attitudes <- tar_read(otm1_attitudes, store = otm1_store)
otm1_iat_lme <- tar_read(otm1_iat2_lme, store = otm1_store)
otm1_mem <- tar_read(otm1_memory, store = otm1_store)
```

(ref:otm1-participant-table) Participant demographics by location.

(ref:otm1-participant-table-note) Mean age is given with range in brackets.

```{r}
#| label: otm1-participant-table

otm1_mem |>
  group_by(Location) |>
  summarize(
    age_mean = mean(Age, na.rm = TRUE)
    , age_min = min(Age)
    , age_max = max(Age)
    , female = apa_num(sum(Gender == "female") / length(Gender) * 100)
    , male = apa_num(sum(Gender == "male") / length(Gender) * 100)
    , nonbinary = apa_num(sum(Gender == "nonbinary") / length(Gender) * 100)
    , n = length(Gender)
  ) |>
  mutate(age = paste0(apa_num(age_mean), " [", age_min, ", ", age_max, "]")) %>%
  select(Location, n, age, female, male, nonbinary) |>
  label_variables(
    n = "$n$"
    , age = "Age"
    , female = "Female (\\%)"
    , male = "Male (\\%)"
    , nonbinary = "Non-binary (\\%)"
  ) |>
  apa_table(
    caption = "(ref:otm1-participant-table)"
    , note = "(ref:otm1-participant-table-note)"
    , align = "lrrrrr"
    , col_spanners = list("Gender" = c(4, 6))
    , escape = FALSE
    , placement = "h"
  )
```


## Mixed model analysis

The ANOVA of IAT scores reported in the main text ignores potential systematic trial-to-trial variability in IAT response latencies due to stimuli.
Any such systematic but unaccounted-for variance can inflate test statistics and yield anticonservative $p$ values as well as underestimated confidence intervals.
We, therefore, also conducted a linear mixed model analysis of response times with crossed random effects for participants and items to ensure that our conclusion are not contingent on inadvertent stimulus effects [for details see @wolsiefer_modeling_2017].
For this analysis we excluded participants with error rates across all blocks larger than 50% or who responded faster than 300 ms on at least 10% of all trials.
We additionally discarded trials in which responses were faster than 400 ms or slower than 10 s.
These exclusion criteria are the same as those used by @wolsiefer_modeling_2017.

We analyzed standardized response latencies, that is, the time that elapsed between stimulus presentation and *correct* response divided by the standard deviation of all response latencies in a given block, Figure\ \@ref(fig:otm1-iat-plot).
To assess the reversal of the response mapping effect, we contrasted the common response mapping of Bob and negative words with the common mapping of Bob and positive words.
Hence, larger values indicate more favorable evaluations.

(ref:otm1-iat-plot) Standardized IAT response latencies across learning blocks.
Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples.

```{r}
#| label: otm1-iat-plot
#| fig-cap: "(ref:otm1-iat-plot)"

otm1_results_legend <- guide_legend(
    # title = "Valence order\nDescriptions of Bob\n(Briefly presented primes)"
    title = expression(atop("Valence order", atop(scriptstyle("Behavioral information"), scriptstyle("(Briefly flashed words)"))))
    , title.position = "top"
    , title.hjust = 0.5
    , reverse = TRUE
    , keyheight = 2
  )

my_labeller <- function(x, ...) label_both(x, sep = " ", ...)

otm1_iat_lme %>%
  mutate(ValenceBlock = ifelse(ValenceBlock == "Positive-negative", " Positive-negative\n(Negative-positive)", " Negative-positive\n(Positive-negative)")) %>%
  ggplot(aes(x = Congruent, y = RTD, group = ValenceBlock, color = ValenceBlock, shape = ValenceBlock, fill = ValenceBlock)) +
  stat_summary(fun = mean, geom = "line", position = position_dodge(0.1)) +
  stat_summary(fun.data = mean_cl_boot, position = position_dodge(0.1), color = "black", fun.args = list(B = 10000)) +
  scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  scale_shape_manual(values = c(21, 23), guide = otm1_results_legend) +
  labs(x = "Response mapping", y = "Standardized response time") +
  facet_grid(~ Block, labeller = my_labeller) +
  theme(
    legend.position = "inside"
    , legend.position.inside = c(0.4, 0.75)
    , strip.background = element_blank()
  )
```

```{r}
#| label: otm1-lmer
#| warning: false

emm_options(
  lmer.df = "satterthwaite"
  , lmerTest.limit = 22384
)

otm1_iat_lmer <- tar_read(otm1_iat_lmer, store = otm1_store)

otm1_iat_lmer_summary <- summary(otm1_iat_lmer)
```

(ref:otm1-lmer-fixed-effects-caption) Fixed effect estimates of the linear mixed model analysis of standardized IAT response times.

(ref:otm1-lmer-fixed-effects-note) The model additionally included random participant and item effects with random intercepts and random slopes for all manipulations during the learning procedure and their interactions.

```{r}
#| label: otm1-lmer-table-fixed-effects

otm1_iat_lmer |>
  apa_print() |>
  (\(x) x$table)() |>
  mutate(
    term = gsub("2", "", term)
    , term = gsub("\\bBlock", "Learning block", term)
    , term = gsub("ValenceBlockPositive-negative", "Valence order", term)
    , term = gsub("Block", " block", term)
    , term = gsub("Text", "", term)
    , term = gsub("Type", " type", term)
    , term = gsub("CongruentBob & positive", "Response mapping", term)
  ) |>
  apa_table(
    caption = "(ref:otm1-lmer-fixed-effects-caption)"
    , note = "(ref:otm1-lmer-fixed-effects-note)"
    , align = "lrrrrr"
    , midrules = c(7, 19, 29)
    , escape = FALSE
    , landscape = TRUE
  )
```

```{r}
#| label: otm1-explore-salience-asymmetry
#| eval: false

# Main effect of response mapping is significant for both image types
otm1_iat_lmer %>%
  emmeans(specs = ~ Congruent | imageType, at = list(imageType = c(-1, 1))) %>%
  pairs()
```


(ref:otm1-lmer-random-effects-caption) Random effect estimates and correlations of the linear mixed model analysis of standardized IAT response times.

(ref:otm1-lmer-random-effects-note) We report the estimated standard deviations in the main diagonals and the correlations in the off-diagnoals. The percentages of variance for the random effects were calculated by dividing each variance component by the total random variance, i.e., the sum of the random-effect variances.

```{r}
#| label: otm1-lmer-table-random-effects

fix_term_names <- function(x) {
  fixed_table <- attr(x, "correlation")
  
  term_names <- colnames(x) |>
    papaja::beautify_terms() |>
    gsub("2", "", x = _) |>
    gsub("\\bBlock", "Learning block", x = _) |>
    gsub("ValenceBlockPositive-negative", "Valence order", x = _) |>
    gsub("Block", " block", x = _) |>
    gsub("Text", "", x = _) |>
    gsub("Type", " type", x = _) |>
    gsub("CongruentBob & positive", "Response mapping", x = _)
  

  diag(fixed_table) <- attr(x, "stddev")
  
  fixed_table <- as.data.frame(fixed_table) %>%
    printnum
  
  fixed_table[lower.tri(fixed_table)] <- ""
  
  dimnames(fixed_table) <- list(
    paste0(1:length(term_names), ". ", term_names)
    , paste0(1:length(term_names), ". ")
  )
  
  fixed_table
}

random_effect_tables <- lapply(otm1_iat_lmer_summary$varcor, fix_term_names)
names(random_effect_tables) <- c("Participant", "Stimulus")

stimulus_effect_names <- colnames(random_effect_tables$Stimulus)

random_variances <- lapply(otm1_iat_lmer_summary$varcor, diag) %>%
  unlist %>%
  unname

variance_explained <- (random_variances / sum(random_variances)) %>%
  printnum(gt1 = FALSE)

random_effect_tables$Participant <- cbind(
  "\\% of variance" = variance_explained[1:nrow(random_effect_tables$Participant)]
  , random_effect_tables$Participant
)

random_effect_tables$Stimulus <- cbind(
  "\\% of variance" = variance_explained[1:nrow(random_effect_tables$Stimulus) + nrow(random_effect_tables$Participant)]
  , random_effect_tables$Stimulus
)

random_effect_tables$Participant[, stimulus_effect_names[!stimulus_effect_names %in% colnames(random_effect_tables$Participant)]] <- ""

apa_table(
  random_effect_tables
  , caption = "(ref:otm1-lmer-random-effects-caption)"
  , note = "(ref:otm1-lmer-random-effects-note)"
  , align = "lcrrrrrrrr"
  , midrules = 5
  , escape = FALSE
  , landscape = TRUE
  , font_size = "small"
)
```

<!-- (ref:otm1-iat-lmer-contrasts) Planned contrasts of changes in congruency effects across learning blocks for the linear mixed model analysis of standardized IAT response times. -->

```{r}
#| label: otm1-lmer-emm

otm1_iat_lmer_emm <- emmeans(
  otm1_iat_lmer
  , ~ Congruent * Block * ValenceBlock
)

otm1_iat_lmer_contrasts <- contrast(
  otm1_iat_lmer_emm
  , list(
    "Negative-positive" = c(1, -1, -1, 1, 0, 0, 0, 0)
    , "Positive-negative" = c(0, 0, 0, 0, 1, -1, -1, 1)
  )
) %>%
  apa_print

# otm1_iat_lmer_contrasts %$%
#   table %>%
#   rename("Valence order" = contrast) %>%
#   apa_table(
#     caption = "(ref:otm1-iat-lmer-contrasts)"
#     , escape = FALSE
#     , row.names = FALSE
#   )
```

In line with the ANOVA results, we found the expected three-way interaction between *Response mapping*, *Valence order*, and *Learning block*, Table\ \@ref(tab:otm1-lmer-table-fixed-effects) and \@ref(tab:otm1-lmer-table-random-effects).
The three-way interaction prompted us to test the differences between response mapping effects in the first and second learning block for each valence order.
We found that response time differences indicated *more* favorable evaluations after the first than after the second block when the behavioral information was first positive and later negative, `r otm1_iat_lmer_contrasts$full_result$Positive_negative`.
Vice versa, response time differences indicated *less* favorable evaluations after the first than after the second block when descriptions of Bob were first negative and later positive, `r otm1_iat_lmer_contrasts$full_result$Negative_positive`.
Again, these results indicate that the rating and IAT scores did not dissociate.


## Bayesian model comparison

We implemented the unconstrained model as a hierarchical linear model that encompasses each of the other models as special cases:

$$
\begin{aligned}
\hat y_{ijk} = & \mu_i + \eta_l x_{1il} + \\
          & (\alpha_i + \tau_l x_{1il}) x_{2j} x_{3k} + \\
          & (\beta_i + \upsilon_l x_{1il}) (1 -  x_{2j}) x_{3k}
\end{aligned}
$$

The model predicts the $i$th participant's response to evaluation measure $j$ in the experimental block $k$.
Responses are predicted as a combination of participant-specific intercepts $\mu_i$ (i.e., habitually higher or lower evaluations), a main effect of the labs $\eta_l$, and participant-specific simple effects of learning block for rating scores ($\alpha_i$) and IAT score ($\beta_i$).
Additionally, we allowed the simple effects to be moderated by the labs ($\tau_l$ and $\upsilon_l$ represent the lab-specific deviations from the overall simple effects).
Participant-specific intercepts and simple effects were modeled as the sum of fixed effects and by-participant random effects, such that $\mu_i = \mathcal{N}(\mu, \sigma_\mu)$, $\alpha_i = \mathcal{N}(\alpha, \sigma_\alpha)$, and $\beta_i = \mathcal{N}(\beta, \sigma_\beta)$.

The model does not include a main effect of evaluative measure because any mean differences between evaluative measures were leveled by the by-measure $z$ standardization.
$x_{1il}$ represents $l$ effect coded variables that indicate which lab participant $i$ belongs to; $x_{2j}$ indicates the evaluative measure (1 for rating score and 0 for IAT score), such that $\alpha_i + \tau_l$ is only relevant for rating scores and $\beta_i + \upsilon_l$ is only relevant for IAT scores; $x_{3k}$ is an effect coded variable that is set to 0.5 for block 1 and -0.5 for block 2.

This model allowed us to place priors on the simple effects (in units of standardized mean differences $d$) for each evaluative measure and implement the theoretically motivated order constraints:

$$
\begin{aligned}
\mathcal{M}_\textrm{No effect}:~ & \delta_\alpha = 0 \\ & \delta_\beta = 0 \\
\mathcal{M}_\textrm{One mind}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{M}_\textrm{Two minds}:~ & \delta_\alpha \sim \textrm{Positive-Half-Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Negative-Half-Cauchy}(r = \sqrt2/2) \\
\mathcal{M}_\textrm{Any effect}:~ & \delta_\alpha \sim \textrm{Cauchy}(r = \sqrt2/2) \\ & \delta_\beta \sim \textrm{Cauchy}(r = \sqrt2/2)
\end{aligned}
$$

Additionally, we placed default multivariate Cauchy priors ($r = \sqrt2/2$) on lab main effects $\eta_l$ as well as on lab effects on evaluative differences between blocks for rating scores ($\tau_l$) and IAT scores ($\upsilon_l$).

To formally assess whether the data from all labs exhibited consistent effects we added another model that enforced the order constraint of $\mathcal{M}_\textrm{One mind}$ and $\mathcal{M}_\textrm{Two minds}$ not only for the average block effects ($\alpha$ and $\beta$) but for each lab individually (i.e., $\alpha_l = \alpha + \tau_l$ and $\beta_l = \beta + \upsilon_l$; $\mathcal{M}_\textrm{One mind everywhere}$ and $\mathcal{M}_\textrm{Two minds everywhere}$).

For the analyses we drew 5 million samples to estimate the postrior distribtution of model parameters.
Because the draws from the posterior distribution are used to estimate the Bayes factors for model comparisons that involve order constraints [@klugkist_inequality_2005], the number of draws implies upper and lower bounds on some of the reported Bayes factors.
Most notably, as a direct consequence of the number MCMC samples the $\textrm{BF}_{\mathcal{M}_\textrm{One mind}/\mathcal{M}_\textrm{Two minds}} \in [1 / (5 \times 10^6), 5 \times 10^6]$.

### Prior sensitivity analysis

Bayesian model comparison by Bayes factors are by definition sensitive to the specified prior distributions.
To ensure that our inference is not contigent on our choice of priors, we conducted prior sensitivity analyses for our key results.

Our choice of piors for the simple effects of learning block for rating scores ($\alpha$) and IAT score ($\beta$) could be viewed as either overly optimistic or pessimistic.
The prior on simple rating score effects places considerable probability mass on effects $d$ < 0.707 although the previously reported effects were very large.
Similarly, placing the same prior on the simple effects for rating and IAT scores could be criticized because the previously reported IAT score effects were considerably smaller than those of rating scores.

```{r}
#| label: otm1-prior-sensitivity-analysis

otm1_prior_sensitivity_analysis <- tar_read(otm1_prior_sensitivity_analysis, store = otm1_store)
```

We, therefore, varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(otm1_prior_sensitivity_analysis$rating)` < r_\alpha < `r max(otm1_prior_sensitivity_analysis$rating)`$ and $`r min(otm1_prior_sensitivity_analysis$iat)` < r_\beta < `r max(otm1_prior_sensitivity_analysis$iat)`$ for rating and IAT scores, respectively.
In light of the results from previous studies, we limited our analysis to combinations where the prior scale was larger for rating than for IAT effects.
To reduce the computational burden of this analysis, we drew 500,000 samples for each model comparison and each combination of prior scales, which implies that the Bayes factors for comparisons involving order constraints are bounded within the range of $[1 / (5 \times 10^5), 5 \times 10^5]$.
The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm1-prior-sensitivity-replication-table).
The Bayes factors were not affected by the scale of the priors to any meaningful degree.
This is because our data are informative enough to overwhelm the priors and because these Bayes factors depend only on the shape and location of the joint posterior distribution [@klugkist_bayesian_2005].


(ref:otm1-prior-sensitivity-replication-table) Results of the prior sensitivity analysis for the Bayesian model comparisons of primary interest.

(ref:otm1-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$.
$r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).

```{r}
#| label: otm1-prior-sensitivity-replication-table

variable_labels(otm1_prior_sensitivity_analysis) <- c(
  "rating" = "$r_\\alpha$"
  , "iat" = "$r_\\beta$"
  , "bf_one_mind_two_minds" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Two minds}}$"
  , "bf_one_mind_any_effect" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Any effect}}$"
)

apa_table(
  otm1_prior_sensitivity_analysis
  , caption = "(ref:otm1-prior-sensitivity-replication-table)"
  , note = "(ref:otm1-prior-sensitivity-replication-table-note)"
  , align = "c"
  , escape = FALSE
)
```



## Recognition task prior sensitivity analysis

```{r}
#| label: otm1-prior-sensitivity-recognition

rec_rscales <- seq(from = 0.25, to = 1, length.out = 5)

rec_bfs <- sapply(
  , X = rec_rscales
  , FUN = function(i, ...) { 
    as.vector(
      ttestBF(
        otm1_mem$Accuracy - 0.5
        , mu = 0
        , rscale = i
        , nullInterval = c(0, Inf)
      )[1]
    )
  }
) |>
  range()

rec_bfs_res <- rec_bfs |>
  apa_num(digits = 2, format = "e") |>
  papaja:::strip_math_tags()
```

To test the robustness of our inference regarding participants recognition accuracy we varied the scale $r$ of the Cauchy prior in a wide interval of $[`r min(rec_rscales)`, `r max(rec_rscales)`]$.
The resulting Bayes factors were $`r rec_bfs_res[1]`< \textrm{BF}_{10} < `r rec_bfs_res[2]`$ and thus varied by a factor of `r rec_bfs[1] / rec_bfs[2]`.
These results again reassure that our inference is robust to a wide range of scales of the default Cauchy prior.


## Word recogniton and IAT score differences

(ref:otm1-rydell-recognition-plot) Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples. Small points represent individual participants' accuracy. Violins represent kernel density estimates of sample distributions.

```{r}
#| label: otm1-rydell-recognition-plot
#| fig-width: 3.5
#| fig-height: 2.5
#| fig-cap: "(ref:otm1-rydell-recognition-plot)"

otm1_mem |>
  ggplot(aes(x = Location, y = Accuracy, shape = Location, fill = Location)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  coord_cartesian(ylim = c(NA, 1)) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Location"
    , y = "Recognition accuracy"
  ) +
  theme(legend.position = "none")
```

In contrast to the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was above chance in this study, Figure\ \@ref(fig:otm1-rydell-recognition-plot).
Memory for these words may, thus, have interfered with the associative learning process and prevented the predicted reversal of IAT score differences between learning blocks.
We, therefore, performed an exploratory regression analysis of IAT score difference and recognition accuracy of briefly flashed words.
Positive IAT score differences indicate a more favorable evaluation after the block in which we presented positive behavioral information and briefly flashed negative words.
If word recognition indeed obstructed the associative learning process, we would expect to observe a positive relationship between the recognition accuracy and IAT score differences between blocks:
When the recognition for briefly flashed words is high, IAT score differences should be positive, that is reflect the valence of the behavioral information.
We would expect to observe smaller and eventually negative IAT score differences as the recognition accuracy declines and associative learning takes over.
To account for measurement error in the recognition accuracy of briefy flashed words we fit an errors-in-variable regression model [@Klauer_Draine_Greenwald_1998].
Because the model assumes that predictor values are sampled from a Gaussian distribution truncated at 0, we probit-transformed the recognition accuracy.^[A standard linear regression analysis yielded the same results.]

(ref:otm1-prime-recognition-iat-difference) Scatterplot of the recognition accuracy of briefly flashed words (on probit scale) and evaluative differences in IAT scores between learning blocks in which Bob was presented with positive descriptions and those in which he was paired with negative descriptions.
The regression line and confidence band represents predictions of the errors-in-variables model [@Klauer_Draine_Greenwald_1998].

```{r}
#| label: otm1-prime-recognition-iat-difference
#| fig-cap: "(ref:otm1-prime-recognition-iat-difference)"
#| message: false

otm1_attitudes_collapsed <- tar_read(otm1_attitudes_collapsed, store = otm1_store) # Collapse across ValcenceOrder
otm1_attitudes_delta <- otm1_attitudes_collapsed %>%
  spread(Block, Attitude) %>%
  mutate(delta = `1` - `2`) %>%
  select(-`1`, -`2`)

otm1_iat_delta <- full_join(otm1_attitudes_delta, select(otm1_mem, ParticipantNumber, Accuracy)) %>% 
  filter(Measure == "IATscore")

otm1_iat_delta %>%
  ggplot(aes(x = Accuracy, y = delta)) +
  geom_hline(yintercept = 0, linetype = "22") +
  geom_vline(xintercept = 0.5, linetype = "22") +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "eiv_lm", color = "black", method.args = list(n.optim = 50)) +
  # geom_smooth(method = "lm", color = "black") +
  labs(
    x = bquote("Recognition accuracy ["~Phi^-1*(italic(p))~"]")
    , y = expression("IAT score difference"~group("[", Delta~italic(z)~score, "]"))
  ) +
  scale_x_continuous(trans = "probit") +
  theme_apa()
```


```{r}
#| label: otm1-prime-recognition-iat-difference-regression

otm1_iat_delta_eiv_lm_res <- otm1_iat_delta %>%
  filter(Measure == "IATscore") %>%
  mutate(Accuracy = qnorm(Accuracy)) %>%
  eiv_lm(delta ~ Accuracy, data = ., n.optim = 50) %>% 
  apa_print
```


We did not detect a relationship between the recognition accuracy of briefly preseted words and IAT score differences between learning blocks, `r otm1_iat_delta_eiv_lm_res$full_result$Accuracy`.
Moreover, the positive intercept of the regression line indicates a positive IAT score difference despite at-chance word recognition accuracy, `r otm1_iat_delta_eiv_lm_res$full_result$Intercept`.
Hence, even for participants who did not recognize the briefly flashed words, IAT score differences reflected the valence of the behavioral information, see Figure\ \@ref(fig:otm1-prime-recognition-iat-difference).
These results provide no indication that the deviation of our findings from those reported by @rydell_two_2006 are attributable to the above-chance recognition of briefly flashed words in this study.

<!--
#### Prime valence memory

```{r listPrimes, echo = FALSE, eval=FALSE}

# correct names of primes
eng_pos <- c("Flower",
            "Friend",
            "Gift",
            "Happy",
            "Puppy",
            "Pretty",
            "Party",
            "Kiss",
            "Kitten",
            "Smile")

eng_neg <- c("Corpse",
            "Death",
            "Hell",
            "Pain",
            "War",
            "Hurt",
            "Spider",
            "Stink",
            "Trash",
            "Ugly")

nl_pos <- c("Bloem",
            "Vriend",
            "Geschenk",
            "Blij",
            "Puppy",
            "Mooi",
            "Feest",
            "Kus",
            "Katje",
            "Glimlach")

nl_neg <- c("Lijk",
            "Dood",
            "Hel",
            "Pijn",
            "Oorlog",
            "Letsel",
            "Spin",
            "Stank",
            "Afval",
            "Lelijk")

ger_pos <- c("Blume",
            "Freund",
            "Geschenk",
            "Glücklich",
            "Welpe",
            "Hübsch",
            "Party",
            "Kuss",
            "Kätzchen",
            "Lächeln")

ger_neg <- c("Leiche",
            "Tod",
            "Hölle",
            "Schmerz",
            "Krieg",
            "Verletzung",
            "Spinne",
            "Gestank",
            "Abfall",
            "Hässlich")


# prep data frame to correspond with correct names

otm1_mem$chosenItems <- gsub("\\r", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("u'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("'", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("\\", "", otm1_mem$chosenItems, fixed = TRUE)
otm1_mem$chosenItems <- gsub("ï»¿", "", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("[", "", otm1_mem$chosenItems, fixed = TRUE) 
otm1_mem$chosenItems <- gsub("]", "", otm1_mem$chosenItems, fixed = TRUE)

otm1_mem$chosenItems <- gsub("xfc", "ü", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xe4", "ä", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xf6", "ö", otm1_mem$chosenItems) 
otm1_mem$chosenItems <- gsub("xdf", "ß", otm1_mem$chosenItems)

otm1_mem <- separate(otm1_mem, 
                     col = "chosenItems", 
                     into = paste0("chosen", 1:20), 
                     sep = ", ")

pos <- c(eng_pos, nl_pos, ger_pos)
neg <- c(eng_neg, nl_neg, ger_neg)
otm1_mem$poscor <- 0
otm1_mem$negcor <- 0


for(i in 1:20){
  otm1_mem$poscor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% pos, otm1_mem$poscor + 1, otm1_mem$poscor + 0)
  otm1_mem$negcor <- ifelse(otm1_mem[, paste0("chosen", i)] %in% neg, otm1_mem$negcor + 1, otm1_mem$negcor + 0)
}

aggregate(negcor ~ Location, data = otm1_mem, FUN = mean)
aggregate(poscor ~ Location, data = otm1_mem, FUN = mean)

t.test(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Ghent")$poscor, y = subset(otm1_mem, Location == "Ghent")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Cologne")$poscor, y = subset(otm1_mem, Location == "Cologne")$negcor, paired = TRUE)

t.test(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)
ttestBF(x = subset(otm1_mem, Location == "Harvard")$poscor, y = subset(otm1_mem, Location == "Harvard")$negcor, paired = TRUE)

```
-->

# Experiment 2

```{r}
#| label: otm2-load-data

otm2_attitudes <- tar_read(otm2_attitudes, store = otm2_store)
otm2_mem <- tar_read(otm2_memory, store = otm2_store)
```

Table\ \@ref(tab:otm2-participant-table) summarizes the participants' demographics separately for each location of data collection.

(ref:otm2-participant-table) Participant demographics by location.

(ref:otm2-participant-table-note) Mean age is given with range in brackets. Missing values for gender cause somevbB  percentages to not sum to 100\%.

```{r}
#| label: otm2-participant-table

otm2_mem |>
  group_by(Location) |>
  summarize(
    age_mean = mean(Age, na.rm = TRUE)
    , age_min = min(Age)
    , age_max = max(Age)
    , female = apa_num(sum(Gender == "female", na.rm = TRUE) / length(Gender) * 100)
    , male = apa_num(sum(Gender == "male", na.rm = TRUE) / length(Gender) * 100)
    , nonbinary = apa_num(sum(Gender == "nonbinary", na.rm = TRUE) / length(Gender) * 100)
    , n = length(Gender)
  ) |>
  mutate(age = paste0(apa_num(age_mean), " [", age_min, ", ", age_max, "]")) %>%
  select(Location, n, age, female, male, nonbinary) |>
  label_variables(
    n = "$n$"
    , age = "Age"
    , female = "Female (\\%)"
    , male = "Male (\\%)"
    , nonbinary = "Non-binary (\\%)"
  ) |>
  apa_table(
    caption = "(ref:otm1-participant-table)"
    , note = "(ref:otm1-participant-table-note)"
    , align = "lrrrrr"
    , col_spanners = list("Gender" = c(4, 6))
    , escape = FALSE
    , placement = "h"
  )
```


## Prior sensitivity analyses

### Bayesian model comparison

```{r}
#| label: otm2-prior-sensitivity-analysis

otm2_prior_sensitivity_analysis <- tar_read(otm2_prior_sensitivity_analysis, store = otm2_store)
```

As for Experiment 1, we varied the scale for the Cauchy priors on the simple effects in the ranges of $`r min(otm2_prior_sensitivity_analysis$rating)` < r_\alpha < `r max(otm2_prior_sensitivity_analysis$rating)`$ and $`r min(otm2_prior_sensitivity_analysis$iat)` < r_\beta < `r max(otm2_prior_sensitivity_analysis$iat)`$ for rating and IAT scores, respectively.
The results of the prior sensitvity analysis reassure us that our inference is robust to a wide range and combination of scales of the default Cauchy priors, see Table\ \@ref(tab:otm2-prior-sensitivity-replication-table).
The Bayes factors were not affected by the scale of the priors to any meaningful degree.


(ref:otm2-prior-sensitivity-replication-table) Results of the prior sensitivity analysis for the Bayesian model comparisons of primary interest.

(ref:otm2-prior-sensitivity-replication-table-note) The Bayes factor (BF) in favor of $\mathcal{M}_\textrm{One mind}$ relative to $\mathcal{M}_\textrm{Any effect}$ is bounded within the range of $[0, 4]$.
$r_\alpha$ and $r_\beta$ denote the scale for the Cauchy prior on the simple effects of learning block for rating scores ($\alpha$) and IAT scores ($\beta$), respectively (in units of standard deviations).

```{r}
#| label: otm2-prior-sensitivity-replication-table

variable_labels(otm2_prior_sensitivity_analysis) <- c(
  "rating" = "$r_\\alpha$"
  , "iat" = "$r_\\beta$"
  , "bf_one_mind_two_minds" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Two minds}}$"
  , "bf_one_mind_any_effect" = "$\\textrm{BF}_{\\mathcal{M}_\\textrm{One mind}/\\mathcal{M}_\\textrm{Any effect}}$"
)

apa_table(
  otm2_prior_sensitivity_analysis
  , caption = "(ref:otm2-prior-sensitivity-replication-table)"
  , note = "(ref:otm2-prior-sensitivity-replication-table-note)"
  , align = "c"
  , escape = FALSE
)
```

## Recognition task prior sensitivity analysis

(ref:otm2-rydell-recognition-plot) Black-rimmed points represent condition means, error bars represent 95% bootstrap confidence intervals based on 10,000 samples. Small points represent individual participants' accuracy. Violins represent kernel density estimates of sample distributions.

```{r}
#| label: otm2-rydell-recognition-plot
#| fig-width: 3.5
#| fig-height: 2.5
#| fig-cap: "(ref:otm2-rydell-recognition-plot)"

otm2_mem |>
  ggplot(aes(x = Duration, y = Accuracy, shape = Duration, fill = Duration)) +
  geom_hline(yintercept = 0.5, color = grey(0.5)) +
  geom_violin(alpha = 0.3) +
  # geom_point(position = position_jitterdodge(jitter.width = 0.1, dodge.width = 0.1)) +
  geom_sina(alpha = 0.5, size = 1) +
  # stat_summary(fun.y = mean, aes(group = Location, linetype = ValenceBlock), geom = "line", position = position_dodge(0.1), color = "black") +
  stat_summary(fun.data = mean_cl_boot, color = "black", fun.args = list(B = 10000)) +
  # scale_color_brewer(palette = "Set1", guide = otm1_results_legend) +
  # scale_fill_brewer(palette = "Set1", guide = otm1_results_legend) +
  coord_cartesian(ylim = c(NA, 1)) +
  scale_shape_manual(values = c(21, 23, 24)) +
  scale_color_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  scale_fill_manual(values = c(RColorBrewer::brewer.pal(3, "Set1"), "#000000")) +
  labs(
    x = "Duration of briefly flashed words (ms)"
    , y = "Recognition accuracy"
  ) +
  theme(legend.position = "none")
```

Mirroring the original results reported by @rydell_two_2006, the recognition accuracy of briefly flashed words was at chance in when flashed for 13 ms, Figure\ \@ref(fig:otm2-rydell-recognition-plot).

```{r}
#| label: otm2-prior-sensitivity-recognition

rec_rscales <- seq(from = 0.25, to = 1, length.out = 5)

rec_bfs <- sapply(
  , X = rec_rscales
  , FUN = function(i, ...) {
    as.vector(
      ttestBF(
        filter(otm2_mem, Duration == "13")$Accuracy - 0.5
        , mu = 0
        , rscale = i
        , nullInterval = c(0, Inf)
      )[1] %>%
        {1/.}
    )
  }
) |>
  range()
```

To test the robustness of our inference regarding participants recognition accuracy we varied the scale $r$ of the Cauchy prior in a wide interval of $[`r min(rec_rscales)`, `r max(rec_rscales)`]$.
The resulting Bayes factors were $`r rec_bfs[1]`< \textrm{BF}_{01} < `r rec_bfs[2]`$ and thus varied by a factor of `r rec_bfs[2] / rec_bfs[1]`.
These results again reassure that our inference is robust to a wide range of scales of the default Cauchy prior.

```{r}
#| label: create-r-references

r_refs(file = "r-references.bib")
```

\newpage

# References

\begingroup
\setlength{\parskip}{0pt}
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
